State Results

### 2023-06-27 reports/county_figures.Rmd
update reports

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by Date$\\,$"

@@

county_dat <- county %>%
  # set Nantucket, Duke fips to Nantucket since we have wastewater data
  # for Nantucket
  left_join(dates,  relationship = "many-to-many") %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate = max(date)) %>%
  ungroup() %>%
  left_join(county_names, by=c('fips'='fips')) %>%
  mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name))

@@

>>>>

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"

@@

county_dat <- county %>%
  # set Nantucket, Duke fips to Nantucket since we have wastewater data
  # for Nantucket
  left_join(dates,  relationship = "many-to-many") %>%
  group_by(biweek) %>%
  mutate(mindate = min(date),
         maxdate = max(date)) %>%
  ungroup() %>%
  left_join(county_names, by=c('fips'='fips')) %>%
  left_join(versions) %>%
  mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name))

@@

county_dat %>%
  filter(fips %in% sample(unique(.data$fips),2))  %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .5,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

### 2023-06-27 reports/priors.Rmd
update reports

ctis %>%
  group_by(state) %>%
  summarize(median = median(beta, na.rm=TRUE),
            mean = mean(beta, na.rm=TRUE),
            q1 = quantile(beta, .025,  na.rm=TRUE),
            q2 = quantile(beta, .975,  na.rm=TRUE)) %>%
  ggplot(aes(x= fct_reorder(state, mean, .desc=TRUE),
             y = mean)) +
  geom_errorbar(aes(ymin=q1,ymax=q2),width=.2) +
  geom_point(color="darkred", size=2) +
  scale_y_continuous(n.breaks=10) +
  labs(y= TeX("Empirical Estimates of $\\beta$"),
       x="State",
       title = TeX("Empirical Estimates of $\\beta$ from the COVID-19 Trends and Impact Survey"),
       subtitle = "2.7% Percentile, 97.5% Percentile, and Mean By State" ) +
  theme_c(axis.title=element_text(size=12))

@@

@@

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c()

>>>>

ctis %>%
  group_by(state) %>%
  summarize(median = median(beta, na.rm=TRUE),
            mean = mean(beta, na.rm=TRUE),
            q1 = quantile(beta, .025,  na.rm=TRUE),
            q2 = quantile(beta, .975,  na.rm=TRUE)) %>%
  ggplot(aes(x= fct_reorder(state, mean, .desc=TRUE),
             y = mean)) +
  geom_errorbar(aes(ymin=q1,ymax=q2),width=.2) +
  geom_point(color="darkred", size=2) +
  scale_y_continuous(n.breaks=10) +
  labs(y= TeX("Empirical Estimates of $\\beta$"),
       x="State",
       title = TeX("Empirical Estimates of $\\beta$ from the COVID-19 Trends and Impact Survey"),
       subtitle = "2.7% Percentile, 97.5% Percentile, and Median By State" ) +
  theme_c(axis.title=element_text(size=12))

@@

```{r}
#
# Logistic transformation of the Beta CDF.
#
f.beta <- function(alpha, beta, x, lower=0, upper=1) {
  p <- pbeta(x, alpha, beta)
 log(p/(1-p))
}
#
# Sums of squares.
#
delta <- function(fit, actual) sum((fit-actual)^2)
#
# The objective function handles the transformed parameters `theta` and
# uses `f.beta` and `delta` to fit the values and measure their discrepancies.
#
objective <- function(theta, x, prob, ...) {
  ab <- exp(theta) # Parameters are the *logs* of alpha and beta
  fit <- f.beta(ab[1], ab[2], x, ...)
  return (delta(fit, prob))
}
#
# Solve two problems.
#
par(mfrow=c(1,2))
alpha <- 15; beta <- 22 # The true parameters
for (x in list(c(1e-3, 2e-3), c(1/3, 2/3))) {
  x.p <- f.beta(alpha, beta, x)        # The correct values of the p_i
  start <- log(c(1e1, 1e1))            # A good guess is useful here
  sol <- nlm(objective, start, x=x, prob=x.p, lower=0, upper=1,
             typsize=c(1,1), fscale=1e-12, gradtol=1e-12)
  parms <- exp(sol$estimate)           # Estimates of alpha and beta
  #
  # Display the actual and estimated values.
  #
  print(rbind(Actual=c(alpha=alpha, beta=beta), Fit=parms))
  #
  # Plot the true and estimated CDFs.
  #      
  curve(pbeta(x, alpha, beta), 0, 1, n=1001, lwd=2)
  curve(pbeta(x, parms[1], parms[2]), n=1001, add=TRUE, col="Red")
  points(x, pbeta(x, alpha, beta))
}
```

```{r}
#
# Logistic transformation of the Beta CDF.
#
f.beta <- function(alpha, beta, x, lower=0, upper=1) {
  p <- pbeta(x, alpha, beta)
 return(p)
}
#
# Sums of squares.
#
delta <- function(fit, actual) sum((fit-actual)^2)
#
# The objective function handles the transformed parameters `theta` and
# uses `f.beta` and `delta` to fit the values and measure their discrepancies.
#
objective <- function(shapes, x, prob, ...) {
  fit <- pbeta(x, shapes[1], shapes[2], ...)
  # return sum of squares
  return(sum((fit, prob)^2))
}

# Solve two problems.

par(mfrow=c(1,2))
alpha <- 15; beta <- 22 # The true parameters
for (x in list(c(1e-3, 2e-3), c(1/3, 2/3))) {
  x.p <- f.beta(alpha, beta, x)        # The correct values of the p_i
  start <- (c(1e1, 1e1))            # A good guess is useful here
  sol <- nlm(objective, start, x=x, prob=x.p, lower=0, upper=1,
             typsize=c(1,1), fscale=1e-12, gradtol=1e-12)
  parms <- (sol$estimate)           # Estimates of alpha and beta
  #
  # Display the actual and estimated values.
  #
  print(rbind(Actual=c(alpha=alpha, beta=beta), Fit=parms))
  #
  # Plot the true and estimated CDFs.
  #      
  curve(pbeta(x, alpha, beta), 0, 1, n=1001, lwd=2)
  curve(pbeta(x, parms[1], parms[2]), n=1001, add=TRUE, col="Red")
  points(x, pbeta(x, alpha, beta))
}

for (x in list(c(.1200,.2188,.3683))) {
  # x.p <- f.beta(alpha, beta, x)        # The correct values of the p_i
  start <- (c(1e1, 1e1))            # A good guess is useful here
  sol <- nlm(objective, start, x=x, prob=c(.025,.5,.975), lower=0, upper=1,
             typsize=c(1,1), fscale=1e-12, gradtol=1e-13)
  parms <- (sol$estimate)           # Estimates of alpha and beta
  #
  # Display the actual and estimated values.
  #
  # print(rbind(Actual=c(alpha=alpha, beta=beta), Fit=parms))
  #
  # Plot the true and estimated CDFs.
  #      
  # curve(pbeta(x, alpha, beta), 0, 1, n=1001, lwd=2)
  # curve(pbeta(x, parms[1], parms[2]), n=1001, add=TRUE, col="Red")
  # points(x, pbeta(x, alpha, beta))
}
parms

rbeta(1e4, parms[1], parms[2]) %>% median()
rbeta(1e4, parms[1], parms[2]) %>% quantile(.025)
rbeta(1e4, parms[1], parms[2]) %>% quantile(.975)

rbeta(1e3, parms[1], parms[2]) %>% mean()

```{r, fig.height=7}

ctis %>%
  group_by(state) %>%
  summarize(median = median(beta, na.rm=TRUE),
            mean = mean(beta, na.rm=TRUE),
            q1 = quantile(beta, .025,  na.rm=TRUE),
            q2 = quantile(beta, .975,  na.rm=TRUE)) %>%
  ggplot(aes(y=fct_reorder(state, mean, .desc=TRUE))) +
  ggridges::geom_density_ridges(
    aes(x=beta,
        y=fct_reorder(state, beta, .fun =median)),
    data=ctis,
    fill="#596281",
    quantile_lines=TRUE,
    quantiles = c(.025,.975),
    quantile_fun=function(beta,...) c(
                                    #  quantile(beta,.025, na.rm=TRUE),
                                      median(beta,na.rm=TRUE)
                                    #  quantile(beta,.975, na.rm=TRUE)
                                      )) +
  # geom_errorbar(aes( xmin=q1,xmax=q2),width=.2) +
  scale_x_continuous(n.breaks=10, limits=c(0,1)) +
  labs(x= TeX("Empirical Estimates of $\\beta$"),
       y="State",
       title = TeX("Empirical Estimates of $\\beta$ from the COVID-19 Trends and Impact Survey"),
       subtitle = "Density Estimate of Distribution and Median by State" ) +
  theme_c(axis.title=element_text(size=12),
          axis.text.x=element_text(size=11))

@@

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density(alpha=.6) +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c()

```{r,include=FALSE}

### 2023-06-27 reports/state_figures.Rmd
update reports

library(tidyverse)
library(targets)
library(here)
library(latex2exp)

@@

# read state-level results
targets_dir <- here("_targets")

state_res <- tar_read(state_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(state_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v4, 
             store =targets_dir)
   )%>%
   bind_rows(
    tar_read(state_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(state_v6,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v7,
             store =targets_dir)
  )

@@

state_res <- state_res %>%
  rename(state=fips) %>%
  left_join(versions) %>%
  mutate(state=toupper(state)) %>%
  left_join(covidestim, relationship= "many-to-many") %>%
  left_join(dates, relationship = "many-to-many")

@@

# Simulation Intervals

@@

@@

# Ratio of Estimated to Observed During Omicron

```{r,results='hide', fig.height=11,fig.width=8}

subset <- state_res %>%
  filter(vlabel == "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$")

@@

subset %>% 
  left_join(codes) %>%
  filter(biweek == 27) %>%
  ggplot(aes(y =fct_reorder(state_name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
  theme(axis.text.y=element_text(size=15),
        axis.text.x = element_text(size=13),
        axis.title = element_text(size = 18),
        plot.subtitle = element_text(size=14)) +
  labs(y="", x="Ratio of Estimated Infections to Observed",
       title ="Ratio of Estimated Infections to Observed Infections\nDuring Omicron",
       subtitle = "December 31, 2021 through January 14, 2022")

@@

>>>>

library(tidyverse)
library(targets)
library(here)
library(scales)
library(latex2exp)
library(cowplot)

@@

# read state-level results
targets_dir <- here("_targets_6_26")

state_res <- tar_read(state_v1, 
                   store =targets_dir) %>% 
  bind_rows(
    tar_read(state_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v4, 
             store =targets_dir)
   )%>%
   bind_rows(
    tar_read(state_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(state_v6,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v7,
             store =targets_dir)
  )

@@

state_res <- state_res %>%
  rename(state=fips) %>%
  left_join(versions) %>%
  mutate(state=toupper(state)) %>%
  left_join(covidestim, relationship= "many-to-many") %>%
  left_join(dates, relationship = "many-to-many")  %>%
  rename(name=state_name) %>%
  group_by(biweek) %>%
  mutate(mindate=min(date),
         maxdate=max(date)) %>%
  ungroup()

state_res <- state_res %>%
  filter(version %in% c("v2", "v5", "v6", "v7"))

@@

# Simulation Intervals Over Time

all_versions <- state_res %>% 
  group_by(state) %>%
  summarize(state_n=n_distinct(version)) %>%
  filter(state_n == max(state_n)) %>%
  pull(state)
```

```{r, eval=FALSE}

state_res %>%
   filter(state %in% sample(unique(all_versions),5))  %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             alpha = .8,
             show.legend=FALSE,
             fill="#596281") +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "By State") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

## Compare Versions

@@

pal <- c("#247C90", "red")

names(pal) <- c(unique(subset$vlabel), "Covidestim")

state_res %>%
   filter(state %in% sample(unique(all_versions),5))  %>% 
  filter(version %in% c("v2", "v5", "v6", "v7")) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .8,
             show.legend=FALSE #,
           #  fill="#596281"
             ) +
   geom_linerange(aes(xmin = mindate,
                      xmax=maxdate,
                      y = positive,
                      color = 'obs'),
                  size=.5) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "By State") +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

@@

## Compare States

```{r, fig.height=11, fig.height=9}

subset %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .8,
             show.legend=FALSE) +
  geom_ribbon(aes(x = date,
                  fill = 'Covidestim',
                  ymin = infections.lo,
                  ymax = infections.hi),
              alpha = .6) +
  facet_wrap(~state, ncol=5, scales = "free_y",
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=6),
          axis.text.y = element_text(size=8),
          legend.position = "top") +
  scale_fill_manual(values =pal,
                    labels = TeX(names(pal)),
                    name='',
                    breaks="Covidestim")  +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))

ggsave(here('figures/intervals-and-covidestim-all-states.pdf'))

## Ratio of Estimated to Observed

```{r, fig.height=10,fig.width=12}

subset %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb/positive,
             ymax = exp_cases_ub/positive,
             fill = vlabel),
             alpha = .9,
             show.legend=FALSE,
             fill= "#247C90") +
  facet_wrap(~state, ncol=5, 
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=6),
          axis.text.y = element_text(size=8),
          legend.position = "top") +
  scale_fill_manual(values =pal,
                    labels = TeX(names(pal)),
                    name='',
                    breaks="Covidestim")  +
  labs(y = "Ratio of Estimated Infections to Observed",
       x="",
       title = paste0("Ratio of Estimated Infections to Observed by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))

ggsave(here('figures/ratio-estimated-to-observed-all-states.pdf'))

# Comparing States at Specific Two-week Intervals

## During Alpha Wave

```{r, fig.height=9,fig.width=8}

plt1 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 7) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Alpha Wave",
       subtitle = "March 26, 2021 through April 8, 2021")

plt1

## During Delta Wave

```{r, fig.height=9,fig.width=8, results='hide'}

subset %>%
  mutate(ratio = exp_cases_median/positive) %>%
  group_by(biweek) %>%
  summarize(mean = mean(ratio),
            mindate=min(date),
            maxdate=max(date)) %>%
  arrange(desc(mean))

```{r, fig.height=9,fig.width=8}

plt2 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 13) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
 theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Delta Wave",
       subtitle = "June 18, 2021 through July 1, 2021")

plt2

## During Omicron Wave

```{r,results='hide', fig.height=9,fig.width=8}

@@

subset %>% 
  left_join(codes) %>%
  filter(biweek == 13) %>%
  pull(date) %>% 
  range()

plt3 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 27) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Omicron Wave",
       subtitle = "December 31, 2021 through January 14, 2022")

plt3

@@

## All Waves Together

```{r, fig.height=10, fig.width=17}

plt <- plot_grid(plt1,plt2, plt3, nrow=1, align="none")

title <- ggplot() +
  labs(title = "Ratio of Estimated Infections to Observed Infections") +
  theme_c(plot.title=element_text(size=25))

plot_grid(title, plt, nrow=2, rel_heights= c(.05,.95))
